### 2018-06-04 manuscript/case12.tex
1st submit to ChinaVis 2018

\section{Case Study}
We apply our method with our data. Two cases are derived to demonstrate the powerness of our method. We believe this work to be one of the nature steps into research of social understanding of the city.

\subsection{Case 1: City Folding}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case111.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case112.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case113.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case114.eps}}}\hspace{5pt}
\caption{XXX of different groups.}
\label{case11}
\end{figure}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case121.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case122.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case123.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case124.eps}}}\hspace{5pt}
\caption{Distributions of home and working space of different groups.}
\label{case12}
\end{figure}

\begin{figure}
\centering
\subfigure[Top aristocracy.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case131.eps}}}\hspace{5pt}
\subfigure[The underclass.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case132.eps}}}\hspace{5pt}
\subfigure[New rich.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case133.eps}}}\hspace{5pt}
\subfigure[Antizen.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case134.eps}}}\hspace{5pt}
\caption{Distribution of ``not essential" activity of different groups.}
\label{case13}
\end{figure}
The most important factors in \textit{Folding Beijing} are wealth and social status. In this case, we select ``income" and ``education" to express the two factors to explore citizens' mobility and city usage.

We deem persons earning more than 300,000 yuan a year are in rich group, while less than 100,000 yuan are in poor group. Persons with undergraduate diploma belong to high education group. So, there are four groups formed. The first one is ``top aristocracy" with high income and education level. Opposite of them, ``the underclass" have lowest income and little education. Group ``new rich" collects people who are rich but have less education. ``Antizen" is a new word to describe people have good education but earn little, which is the fourth group.

Fig. \ref{case11} shows the top 13 persons' images in each group. Except for income and education, other social features describe every group in different ways. As shown, nearly all of ``top aristocracy" are locals owing house and car. On the contrary, ``the underclass" do not owe local residence, neither the house and car. ``New rich" can afford house. Most of them are in service industry.

To understand how citizens live in the city, there are two crucial aspects to be known: during the night where they sleep, and where do they go during the daytime.
We divide daytime mobility activities into ``essential activity" and ``no essential activity" two categories to capture movement patterns. ``Essential activity" is made up with ``go to work", ``go to school" and ``go back home". Movements with other purposes are ``not essential". People do these movement activities due to their personal willingness and living patterns. Therefore, ``home location", ``working location" and ``not essential" activity space outline one's living space. Our system meets this requirement.

Fig. \ref{case12} shows examples of living space of the four groups. Fig. \ref{case12}(a) and Fig. \ref{case12}(b) show the distributions of home and working space. These two distributions are similar in four groups. ``Top aristocracy" and ``new rich" live concentrated in downtown area of Shenzhen, where the living cost is higher, especially the housing cost. ``The underclass" distribute dispersively all over the whole city. Compared to the rich, the outer space are prefered because of the lower living cost. Lots of ``antizen" live in Nanshan District. There are many universities and high-tech industrial parks are located in Nanshan which attracts good educated persons. The distribution of ``not essential activity" is shown in Fig. \ref{case13}. From the dimension of space, ``new rich" prefer to live in the west of the city. They do not go south east in most times. Other three groups reach the whole city. The height of the bar stands for the percentage of ``not essential activity" in the whole activities. Higher height means that the group has more willingness and cost more time in ``not essential activity", while lower height means more time on work. Comparing four groups, it can be seen that the poor spend more time on work, especially ``the underclass". Working percentage is really small in group ``new rich". They have diverse lives because they do many other things except for working.

\subsection{Case 2: Home-work Distance}
\begin{figure}
\centering
\subfigure[Group of people whose income more than 500,000yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case21.eps}}}\hspace{5pt}
\subfigure[Group of people whose income between 200,000 yuan to 300,000 yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case22.eps}}}\hspace{5pt}
\subfigure[Group of people whose income less than 100,000yuan per year.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case23.eps}}}\hspace{5pt}
\subfigure[Group of people who owe house.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case24.eps}}}\hspace{5pt}
\subfigure[Group of people who rent house.]{
\resizebox*{4.4cm}{!}{\includegraphics{pictures/case25.eps}}}\hspace{5pt}
\caption{Home-work distances of different groups.}
\label{case2}
\end{figure}
Home-work space and commuting behavior is an important concept in economics, geography and sociology. It is influenced by many factors like transportation, housing, land using, etc. Understanding it helps know how city functions for a better planning. In this case, we use a graph of ``working space and commuting distance" to demonstrate our system's help in movement behavior understanding.

We use ``income" and ``have house" to distinguish citizens and learn their home-work distance. Fig. \ref{case2} shows examples of five groups. Fig. \ref{case2}(a), Fig. \ref{case2}(b) and Fig. \ref{case2}(c) are formed according to ``income". They are ``more than 500,000 yuan", ``200,000 to 300,000 yuan" and ``less than 100,000 yuan" levels separately. Fig. \ref{case2}(d) and Fig. \ref{case2}(e) are for group of people ``owing house" and ``rent house".

The height of the bar stands for working frequency of the TAZ. From the figure, it is seen that the working locations are mainly in three areas which are circled in white in Fig. \ref{case2}(c). Space in green circle is another hot working area which only are preferred by the poor.

The color of the bar stands for home-work distance of people working in the TAZ. On the whole, home-work distance is short in Shenzhen for most of the TAZs with different groups have darker color, especially in downtown. When focusing on downtown area, it is seen that there are differences between Futian District with the other two. By comparing three groups distinguished by income, it takes more time to work in Futian District with the decrease of the income. Meanwhile, the opposite is true in others. In combination with Fig. \ref{case2}(d) and Fig. \ref{case2}(e), we find that Nanshan District and Luohu District belongs to all but Futian District belongs to the rich. The poor could rent house living in Nanshan and Luohu to enjoy short home-work distance. In Futian, only the rich working there have short home-work distance. There may be no much housing for rent.

>>>>

\section{Case Study}

In this section, we apply the method described above to study the case of Shenzhen. We introduce the several cases to demonstrate the usage and effectiveness of the system.

%The cases of analysis how individuals use the city are derived to demonstrate the powers. We believe this work would be one of the natural steps into research of social understanding of the city.

\subsection{Case 1: Work-life Balance VS Income/Education}

% \begin{figure}
% \centering
% \subfigure[Top aristocracy.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case111.eps}}}\hspace{5pt}
% \subfigure[The underclass.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case112.eps}}}\hspace{5pt}
% \subfigure[New rich.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case113.eps}}}\hspace{5pt}
% \subfigure[Antizen.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case114.eps}}}\hspace{5pt}
% \caption{XXXXXX of different groups.}
% \label{case11}
% \end{figure}

% \begin{figure}
% \centering
% \subfigure[Top aristocracy.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case121.eps}}}\hspace{5pt}
% \subfigure[The underclass.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case122.eps}}}\hspace{5pt}
% \subfigure[New rich.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case123.eps}}}\hspace{5pt}
% \subfigure[Antizen.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case124.eps}}}\hspace{5pt}
% \caption{}
% \label{case12}
% \end{figure}

This work is inspired and motivated by the implication in science fiction~\textit{Folding Beijing}, which is that people are categorized into three classes and behave in the parallel spatial-temporal patterns. The first cast explores whether the folding city exists in reality or not.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_1}
 \caption{Four Groups Divided by Income and Education Characteristics}
 \label{case11}
\end{figure}

Although it is incomplete, income and education are two of the most essential characteristics to tag an individual with a good resource or not. 
As Figure~\ref{case11} shows, taking income and education as the two dimensions, taking 300K yuan as the border between high and low income and an undergraduate bachelor degree as the border between high and low education level, four different groups are generated in the four quadrants. In the first quadrant, individuals are rich and well educated, who are in a group of so-called \textit{top aristocracy}. The second quadrant holds the group of \textit{new rich}, i.e., individuals with high income but low education income. In the third quadrant, they are the \textit{underclass} who has both low income and education level. The fourth quadrant is \textit{Antizen}, which is a new word to describe people have a good education but earn little.

Figure~\ref{case11} shows the top 12 profiles with the maximum population in each group. In each group, other characteristics surprisingly demonstrate the high correlation to income and education. For example, almost all of the \textit{top aristocracy} is with the residential license,  house, and car. On the contrary, \textit{underclass} do not have the residential license residence, neither the house nor the car. Most of \textit{New rich} has a house and work in the service industry.

Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups. As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost. A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown. The \textit{underclass} distribute more dispersively all over the whole city. Compared to the rich, they prefer the outer space because of the lower living cost. Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home Distributions of the Four Groups}
 \label{case12}
\end{figure}

% To understand how citizens live in the city, there are two crucial aspects to be known: during the night where they sleep, and where do they do during the daytime. ``Home location" could answer the first question. The second one is harder to summarise because of the complexity of daytime activities. In our method, we divide daytime mobility activities into

To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends. Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories. Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''. Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}. It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups. To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups. Figure~\ref{case13}(b) shows three slices. It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}. Working percentage is very small in-group \textit{new rich}. They live a more diverse lifestyle because they do many other things (the pink ones) except working.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_3}
 \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
 \label{case13}
\end{figure}

% By comparing them, it can be seen that the poor spend more time on work, especially ``the underclass". Working percentage is really small in-group ``new rich". They have diverse lives because they do many other things except for working.

% \begin{figure}
%   \centering
%   \includegraphics[width=0.95\linewidth]{pictures/case1_4}
%   \caption{Examples of XXXXX.}
%   \label{case14}
% \end{figure}
% two categories to capture mobility patterns. ``routine activity" is made up with ``go to work", ``go to school" and ``go back home". Movements with other purposes are ``not essential". People do these movement activities due to their personal willingness and living style. Therefore, ``home location", ``working location" and ``not essential" activity space outline one's living space. Our system meets this requirement.

% In Fig. \ref{case13}, the distributions of ``essential" activity including ``go to work" and ``go home", and ``not essential activity" are shown.

% From the dimension of space, ``new rich" prefer to live in the west of the city. They do not go south-east in most times. Other three groups reach the whole city. The height of the bar stands for the percentage of each kind of activity. Higher height means that the group has more willingness and cost more time in ``, not the essential activity", while lower height means more time on work. As we described in Section XXX, 遮挡问题, 我们使用切面解决。 Fig. \ref{case14} give three examples within each group to check the detailed information in the 2.5D graph. By comparing them, it can be seen that the poor spend more time on work, especially ``the underclass". Working percentage is really small in-group ``new rich". They have diverse lives because they do many other things except for working.

\subsection{Case 2: Home-work Distance VS Income/House}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case2}
\end{figure}

% \begin{figure}
% \centering
% \subfigure[Group of people whose income more than 500,000yuan per year.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case21.eps}}}\hspace{5pt}
% \subfigure[Group of people whose income between 200,000 yuan to 300,000 yuan per year.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case22.eps}}}\hspace{5pt}
% \subfigure[Group of people whose income less than 100,000yuan per year.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case23.eps}}}\hspace{5pt}
% \subfigure[Group of people who owe house.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case24.eps}}}\hspace{5pt}
% \subfigure[Group of people who rent house.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/case25.eps}}}\hspace{5pt}
% \caption{Home-work distances of different groups.}
% \label{case2}
% \end{figure}

Home-work distance is an essential metric in economics, geography, and sociology. It refers to the distance between house and workplace. It is influenced by many factors like transportation, housing, land use, etc. Understanding the home-work distance of a region helps to evaluate whether the region is well planned or not. In this case, we demonstrate our system's help in home-work distance understanding.

Considering income potentially determines where people live, we use income as the characteristics to select three groups, the group over 500K, the group during 200-300K and the group less than 100K. In Figure~\ref{case2}, the height of the bar stands for visiting frequency of the TAZ and its color encodes the average home-work distance, red for close and yellow for far. As Figure~\ref{case2}(a) shows, for all the three groups in different income levels, most of the TAZs have dark red or red color which indicates the home-work distance is generally short, especially in downtown. Only those with less than 100K salary work outside the center, such as the space in the green circle. When comparing the three groups in the downtown area, it is seen that it takes more time to go to work in Futian District as the decrease of the income.

We explore the home-work distance of groups with and without a house. 
Figure~\ref{case2}(b) shows the close-up views. It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house. Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.

  % District belongs to all but Futian District belongs to the rich. The poor could rent house living in Nanshan and Luohu to enjoy short home-work distance. In Futian, only the rich working there have short home-work distance. There may be no much housing for rent.

 % From the figure, it is seen that the working locations are mainly in three areas which are circled in white in Fig. \ref{case2}(c). Space in green circle is another hot working area which only is preferred by the poor.
% On the whole, home-work distance is short in Shenzhen for most of the TAZs with different groups have a darker color, especially in downtown. When focusing on the downtown area, it is seen that there are differences between Futian District with the other two. By comparing three groups distinguished by income, it takes more time to work in Futian District with the decrease of the income. Meanwhile, the opposite is true in others. In combination with Fig. \ref{case2}(d) and Fig. \ref{case2}(e),

\subsection{Case 3: Life-style VS Jobs}

% \begin{figure}
% \centering
% \subfigure[Officer.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/311.eps}}}\hspace{5pt}
% \subfigure[Workman.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/321.eps}}}\hspace{5pt}
% \subfigure[Student.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/331.eps}}}\hspace{5pt}
% \subfigure[Businessman.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/341.eps}}}\hspace{5pt}
% \caption{Percentage of movement with purposes in group of different jobs.}
% \label{case31}
% \end{figure}

In this case, we explore the correlation between mobility patterns with the job, to see whether the job has an impact on the movement. Officer, workman, student, and businessman are selected as examples and the population of trips for certain purposes is shown In Figure~\ref{case3}. The height of bars encodes the amount of visit to each TAZ, and color encodes the traveling purpose. There are 10 different kinds of traveling purposes. For quick linking between color and purposes, the regular trips such as go to work, school and home are dyed in cold color, and the irregular trips such as go shopping, hospital, etc, are dyed in the warm color. As Figure~\ref{case3} shows, for officers, the TAZs changes dramatically in height. Some TAZs have much more visiting than others because officers are more constrained to work in some buildings than individuals with other jobs. The relative percentage of irregular activity differs for the four groups. For Workman, about 80 percent of movements are the regular purpose, either go to work or go back home. For students, the percentage becomes to be about 50 percentage. Compared to them, officer and businessman have more flexible and diversified lifestyle.

% Each social attribute has an impact on movement patterns. There are 9 kinds of jobs in the data which offers rich information. Therefore, in this case, we use ``job" as the target social attribute to explore its influence on citizens' movement patterns.

% At first, with 2.5D spatial visual form, we learn what people move for and the percentage of movements with a given purpose.

% The height of each bar stands for the number of movements to the TAZ. Purposes are encoded in color as the legends show. From the perspective of the height of bars, it is seen that the amount of visitors to each TAZ of officers is really different. Several TAZs have the dominant visiting. In Figure~\ref{case3}(a), the heights of yellow bars and rose red bars in different TAZs have great differed. This phenomenon is not that obvious in other three groups. In addition, the percentage of ``not essential" activity differs. For Workman, about 80 percent of movements are ``essential" ones. For students, the percentage becomes to be about 50 percentage. Compared to them, officer and businessman have more flexible and diversified lives.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case3}
\end{figure}

Next, we concentrated on one purpose to see whether it is related to jobs. Here we use ``dinner or entertainment" as the example. As Fig \ref{case32} shows, the height of TAZ bars represents the visiting amount of trips for dinner or entertainment. Color stands for moving distance to reach this TAZ. As we can see, officers prefer to entertain in the downtown area, while workmen cover a larger area. Students tend to concentrate on Nanshan district, probably near schools. For the businessmen, they go lots of places for dinner or entertainment. The biggest difference with other groups is that they would travel a long distance to go somewhere far from downtown areas.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}

% \begin{figure}
% \centering
% \subfigure[Officer.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/314.eps}}}\hspace{5pt}
% \subfigure[Workman.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/324.eps}}}\hspace{5pt}
% \subfigure[Student.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/334.eps}}}\hspace{5pt}
% \subfigure[Businessman.]{
% \resizebox*{4.4cm}{!}{\includegraphics{pictures/344.eps}}}\hspace{5pt}
% \caption{}
% \label{case32}
% \end{figure}

### 2018-06-04 manuscript/data.tex
1st submit to ChinaVis 2018

The advent of mobile sensing techniques makes it possible to develop urban geography from social media source. Complementary to the conventional census, social media brings the benefit of larger sampling frequency and higher disaggregate in terms of space and time. It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.

@@

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolis in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).

\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and deomgraphic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

@@

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)). Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}.

To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).

@@

Over the releasing time period from \m{2016-11 to 2018-01}, 21435 individules (48\% females and 52\% males) were reached and \m{229155} trips are collected. The majority of our 25481 volunteers contribute \m{11} trips averagly.

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of individuals in the city.

Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of all ages, dominately between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high. The technical college and university dominates the education at the 61\% occupancy rate.

@@

Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, bussinessmen. The covering of jobs is pretty wide. Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200 000. Some individuals with higher salary are also reached in our census.

@@

Figure~\ref{fig:data_geometry} shows the basic statistics related to trips. In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common sense of urban life. There are obvious morning and late afternoon peaks. Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with traveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going hospital, etc. Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations spot. It is found that more trips uploaded by volunteers located in Futian and Nanshan districts, the city's heart part of than the surrounding outer areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

@@

Because there is always unevitable bias inherent in fully representing the ground true of society awide, the prelimeary statistical analysis shows positive sign of a relatively even sampling of the population. 
% As a note, although it is a subset of all people with

>>>>

The advent of mobile sensing techniques and social media applications makes it possible to collect spatial data from the social media source. Complementary to the conventional census, it brings the benefit of larger sampling frequency and a broader range in terms of space and time. It is possible to reach a wide range of individuals and collect the movement in human inactive time, such as the mid-night.

@@

In this work, we perform the census survey in Shenzhen, which is one of the most modern metropolia in China. The experiment is deployed on Wechat, a widely used social media application. Figure~\ref{fig:app} shows the data collecting interfaces. Each individual hands in his or her personal characteristics. For privacy issue, all detailed personal information are desensitized to categorical levels (Figure~\ref{fig:app}(a)).

\textbf{Individual Characteristics} Figure~\ref{fig:data_over} lists the \textit{eight domains}, including social, economic and demographic aspects, to give a generalized description of the individual characteristics. The profile will serve as the ingredients for the analysis of mobility patterns over diverse individuals.

@@

\textbf{Traveling Trips} Besides to those individual characteristics, each individual can upload dynamic traveling trips (Figure~\ref{fig:app}(b)). Each trip requires the information of \textit{start/end location}, \textit{start/end time}, \textit{traveling purpose}. To encourage the trip uploading, a credit system retains the contribution of individuals on trips and rewards the volunteers with the top credits (Figure~\ref{fig:app}(c)).

@@

Over the releasing time period from \m{2015-11 to 2016-01}, 21435 individuals (48\% females and 52\% males) were reached and \m{229155} trips are collected. Each volunteer contributes \m{11} trips average.

Our case-study data is confined to a small proportion of Wechat users who opt to contribute their information and trips.
Considering the caveat that self-selecting individuals are most unlikely to represent any clearly defined population~\cite{Longley2015}, we performed a series of preliminary statistics to check whether it is rich enough to represent a wide range of the population in the city.

Figure~\ref{fig:data_age_edu} gives the distribution of age and education over the population. It shows that samples cover a wide range of ages, dominating between 18 to 45. There is also a few records pertaining to individuals below the age of 18 or above 70. The distribution follows the fact that Shenzhen is a city where the majority is young people. According to the 2015 Annual Census Statistics report\footnote{http://www.sztj.gov.cn/xxgk/tjsj/pcgb/201606/t20160614\_3697000.htm}, people aging 15-64 occupy 83.23\% and the median age is 31.5. Figure~\ref{fig:data_age_edu} gives the distribution of education levels, ranging from low to high. The technical college and university dominate the samples at the 61\% occupancy rate.

@@

Figure~\ref{fig:data_job_inc}(a) shows the job types of sampled individuals, who are servants, workers, officers, businessmen and so on. The covering of jobs is pretty wide. Figure~\ref{fig:data_job_inc}(b) gives the radar diagram of the annual pay. The majority get paid below 200 000. Individuals with higher salary are also reached in our census.

@@

Figure~\ref{fig:data_geometry} shows the basic statistics related to trips. In Figure~\ref{fig:data_geometry}(a), the active traveling time (here, we take the start time as the representative of active time) follows the common knowledge of urban life. There are obvious morning and late afternoon peaks. Figure~\ref{fig:data_geometry}(b) gives the counting of different traveling purposes. 95\% trips are tagged with clear raveling purpose in the data. 33\% are going home and 37\% are going to work. Besides this kind of routine traveling, there are also substantial trips such as going shopping, going the hospital, etc. Figure~\ref{fig:data_geometry}(c) shows the spatial distribution of the origins and destinations. It is found that more dots are located in Futian and Nanshan districts, the city's heart than the surrounding areas. This is consistent to Batty's exposition of the focus of city networks and interaction patterns~\cite{batty2013new}.

@@

Because there is always inevitable bias inherent in fully representing the ground truth of the population, the preliminary statistical analysis shows positive sign of a relatively even sampling of the population. 
% As a note, although it is a subset of all people with

### 2018-06-04 manuscript/relatedwork.tex
1st submit to ChinaVis 2018

This work concerns to the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presense of geo-tagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data, but focus more on individual charecteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related work do.

@@

 With the development of location-acquistion techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mining trajectory~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytic, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} et al. construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behaviour based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behaviour among multiple routes.

@@

As the prevence of social medial serivces, social media data with geo-tags are collected to track people's movements in daily lifes. As an analogue of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layouts, to investigate how information flow among multiple places. Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploraiton of sparcely sampled trajectory from social media. Some other researches tend to infer real information, such as names, gender, etc~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\cite{luo2016explore} derive race, gender and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, wrong infering is inevitable. Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.

>>>>

This work concerns the research topic of spatial data visual analytics. Spatio-temporal data has three components, i.e., spatial, temporal and thematic~\cite{andrienko2013visual}. Lots of related work focus on the spatio-temporal analysis in movement data, in the absence of thematic information. The presence of geotagged social media data flourishes the exploration of thematic information along with movement. By analyzing the texts, those work explain what drive the moving activities or what is resulted from. This work continues the thematic research in movement data but focuses more on individual characteristics. Landed by a census experiment, this work is able to analyze the profile information directly, to get rid of indirect data inferred from social media data as other related works do.

@@

 With the development of location-acquisition techniques, massive spatial trajectories are collected, to keep track of the trajectories of various moving objects. Many techniques have been proposed to process, mine trajectory~\cite{Zheng2015_trajectory}. In the field of visualization and visual analytics, spatial visualizations are specifically designed for the time, locations, spatial-temporal information and other properties in the traffic data~\cite{chen2015survey}. A large number of visual analytics tools and applications cover situation-aware exploration, pattern discovery and traffic situation monitoring. Wang et al~\cite{wang2013visual} extract the traffic jam propagation graph extraction to reveal underlying data patterns. Guo et al.~\cite{guo2011tripvista} and Zeng et al.~\cite{zeng2013visualizing} construct geographical regions and visually aggregate the in-between movements as flows. To discover the route travel patterns, Lu et al.~\cite{lu2015trajrank} propose TrajRank to explore the route travel behavior based on ranking. For multiple routes, Liu et al.~\cite{liu2011_routediversity} study the route diversity between locations and Lu et al.~\cite{Lu2017_multipleroute} explore the route choice behavior among multiple routes.

@@

As the presence of social media services, social media data with geo-tags are collected to track people's movements in daily lives. As an analog of remote sensing data in social science research, the geospatial big data has been proposed as social sensing ~\cite{liu2015social}. Hence, analyzing movement information along with rich text has become a hot research area in recent years. Those works infer thematic information from the semantic texts. Cao et al.~\cite{cao2012whisper} propose \textit{Whisper} for tracing the pathways of tweets on a spatial hierarchical layout, to investigate how information flow among multiple places. Krueger et al.~\cite{krueger2014visual} used GPS and location-based service data to support the analysis of movement behaviors. Chen et al.~\cite{chen2016interactive} present a visual analytics system to support the exploration of sparsely sampled trajectory from social media. Some other researchers tend to infer real information, such as names, gender, etc, from social media data~\cite{peddinti2014internet}, to break down the demographic characteristics of social media users. Luo et al.~\cite{luo2016explore} derive race, gender, and age as three demographics dimensions to analyze its impact on the urban human mobility patterns. Since real information is not enforced in social media, the wrong inferring is inevitable. Longley et al.~\cite{Longley2015}~\cite{Paul2016_twitter} identifies and assess the biases inherent in social media usage in social research and evaluate the deployment of social media data in research applications.
